---
title: "Zhong_Jack_HW4"
author: "Jack Zhong"
date: "2016/10/3"
output: html_document
---

## **R Intro** 

***


####__1. Create	the	vectors:__  
   * __a) (1,2,3,...,19,20)__  
```{r}
   1:20
```
&nbsp;

   * __b) (20,19,...,2,1)__  
```{r}
   20:1
```
&nbsp;

   * __c) (1,2,3,...,19,20,19,18,...,2,1)__  
   *thought: create the list from 1 to 20, then add 19 to 1*
```{r}
   c(1:20, 19:1)    
```  
&nbsp;
        
   * __d) (4,	6, 3)	and	assign it	to the	name	tmp.__  	
```{r}
   tmp <- c(4, 6, 3)
```
&nbsp;

   * __e) (4,6,3,	4,6,3,...,4,6,3) where there are 10 occurrences	of 4.__   
   *thought: ten reps of tmp* 
```{r}
   rep(tmp, 10)
```
&nbsp;
              
   * __f) (4,6,3,4,6,3,...,4,6,3,4) where there are 11 occurrences	of 4, 10 occurrences of 6 and	10 occurrences of	3.__    
   *thought: When it reaches 31st repetition, it stops.*
```{r}
    rep(tmp, len=31)
```  
&nbsp;
    
   * __g) (4,4,...,4, 6,6,...,6, 3,3,...,3) where	there	are	10 occurrences of	4, 20 occurrences	of 6 and 30 occurrences	of 3.__  	
```{r}
    rep(tmp,times=c(10,20,30))
```
&nbsp;

&nbsp;

####__2. Create	a	vector of the	value of $e^xcos(x)$ at x	=	3,3.1,3.2,...,5.9,6__
```{r}
    x = seq(3,6, by=.1)
    c(exp(x)*cos(x))
```
&nbsp;

&nbsp;

####__3. Create the following vectors:__
   * __a) ($0.1^30.2^1,0.1^60.2^4,0.1^90.2^7,...,0.1^{36}0.2^{34})$__    
   *thought: View it as two parts: 0.1 to ath power times 0.2 to the bth power*  
```{r}
    a = seq(3,36,by=3)
    b = seq(1,34,by=3)
    c(0.1^a*0.2^b)
```
&nbsp;

   * __b) ($2$,$2^2/2$,$2^3/3$,...,$2^{25}/{25}$)__
   *thought: Note that denominator is the same as the power*  
```{r}
    c = 1:25
    c(2^c/c)
```
&nbsp;

&nbsp;
   
####__4. Calculater the following:__  
   * __a) $\sum_{i=10}^{100} i^3+4i^2$__   
   *thought: Well, just add it up. Typing the formula above is more difficult:)*  
```{r}
    i = 10:100
    sum(i^3+4*i^2)
```
&nbsp;

   * __b) $\sum_{i=1}^{25} 2^i/i+3^i/i^2$__  
   *thought: Add it up again...*   
```{r} 
    i = 1:25
    sum(2^i/i+3^i/i^2)
```
&nbsp;

&nbsp;

####__5. Use	the	function	paste	to	create	the	following	character	vectors	of length	30:__  
   * __a) ("label	1",	"label	2", ..., "label	30"). Note that there is a single	space	between	label	and	the	number following.__  
   *thought: Get the same format with 'label'+ a space + ordered number*  
```{r}
    paste("label", 1:30, sep=" ")
```
&nbsp;

   * __b) ("fn1",	"fn2",	...,	"fn30"). In this case, there is	no space between fn and	the	number following.__	 
   *thought: Get the same format with label, number, separated by nothing*   
```{r}
    paste('fn', 1:30, sep="")
```
&nbsp;

&nbsp;
        
    
####__6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the intergers 0,1,...,999. Both vectors have length 250__
```{r}
    set.seed(50)
    xVec <- sample(0:999, 250, replace=T)
    yVec <- sample(0:999, 250, replace=T)
```
&nbsp;

   * __a) Create the vector ($y_2$$-$$x_1$,...,$y_n$$-$$x_{n-1}$)__   
   *thought: use [-1] to cut off the first number and [-250] cuts off the last one*
```{r}
    yVec[-1]-xVec[-250]
```
&nbsp;

   * __b) Create the vector ($sin(y_{1})/cos(x_{2}$),$sin(y_{2})/cos(x_{3}$),...,$sin(y_{n-1})/cos(x_{n}$))__  
   *thought: Similarly, make sure that we need two sets with same amount of data.*  
```{r}   
    sin(yVec[-250])/cos(xVec[-1])
```
&nbsp;
          
    
   * __c) Create the vector ($x_{1}+2x_{2}-x_{3},...,x_{n-2}+2x_{n-1}-x_n$)__  
   *thought: We dont need the last 2 number from xVec for the 1st element; first and last for the 2nd element; first 2 for the 3rd element*
```{r}
    xVec[-c(249,250)]+2*xVec[-c(1,250)]-xVec[-c(1,2)]
```
&nbsp;
    
   * __d) Calculate $\sum_{i=1}^{n-1} {e^{-x_{i+1}}/(x_{i}+10)}$__ 
   * thought: numerator x2 to x250, denominator x1 to x249
```{r}
    sum(exp(-xVec[-1])/(xVec[-250]+10))
```
&nbsp;

&nbsp;
    
####__7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.__  
   * __a) Pick out the values in yVec which are > 600.__  
```{r}
    yVec[yVec>600]
```
&nbsp;

   * __b) What are the index positions in yVec of the values which are > 600?__  
```{r}
    which(yVec>600)
```
&nbsp;

   * __c) What are the values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)__ 
```{r}
    xVec[yVec>600]
```
&nbsp;

   * __d) Create the vector ( |x1 ??? ????|1/2, |x2 ??? ????|1/2, . . . , |xn ??? ????|1/2) where ????
#    denotes the mean of the vector x = (x1,x2,...,xn).
     sqrt(abs(xVec-mean(xVec)))

#    e) How many values in yVec are within 200 of the maximum value of
#    the terms in yVec?
     sum(yVec>max(yVec)-200)
     
#    f) How many numbers in xVec are divisible by 2? (Note that the mod
#    operator is denoted %%.)
     sum(xVec%%2==0)

#    g) Sort the numbers in the vector xVec in the order of increasing values
#    in yVec.
     xVec[order(yVec)]
#                    we cannot use sort here because we just need the order and apply it to xVec

#    h) Pick out the elements in yVec at index positions 1,4,7,10,13,.
     yVec[c(T,F,F)]
#                    first item good, second, third disposed, and repeat this

#8.  By using the function cumprod or otherwise, calculate:     
     1 + sum(cumprod(seq(2,38,by=2))/seq(3,39,by=2))
#                    first 1 is not in the sequence, after that, they are all multiplication with a specific rule
